Mahotas: Open source software for scriptable computer vision

### 2013-05-02 paper.tex
ENH Update date. Add another ref for mahotas use

\title{Mahotas: Open source software for scriptable computer vision}
\author{Luis Pedro Coelho\\
Lane Center for Computational Biology, Carnegie Mellon University\\
Instituto de Medicina Molecular}
\date{January 2013}

@@

This package (or earlier versions of it) have been used by
myself~\citep{Coelho2009,Coelho2010a} and close collaborators in several
publications~\citep{omerosearcher}. Other groups have used it in published
work, both in cell image analysis~\citep{CYTO:CYTO22034} and in other
areas~\citep{springerlink:10.1007/978-3-642-32335-5_2,ADFM:ADFM201300091}.

>>>>

\title{Mahotas: Open source software for scriptable computer vision}
\author{Luis Pedro Coelho\\
Lane Center for Computational Biology, Carnegie Mellon University\\
Instituto de Medicina Molecular\footnote{Current Address: European Molecular
Biology Laboratory (EMBL), Heidelberg, Germany.}}

\date{May 2013}

@@

This package (or earlier versions of it) have been used by
myself~\citep{Coelho2009,Coelho2010a} and close collaborators in several
publications~\citep{omerosearcher}. Other groups have used it in published
work in cell image analysis~\citep{CYTO:CYTO22034} and in other areas
\citep{springerlink:10.1007/978-3-642-32335-5_2}. \citet{ADFM:ADFM201300091}
used mahotas to detect nanoparticles in electron microscopy images.

Mahotas provides many basic tools which can be combined to process images. It
can be used in any problem which requires the processing of images to extract
quantitative information.
